Dissertation Manuscript

### 2023-10-19 HTW.qmd
fix docx and html. Update htw with embed

[Working Draft of HTW Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}
```{r}
pacman::p_load(tidyverse,knitr,kableExtra)

>>>>

[Working Draft of HTW Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}

![htw](https://tegorman13.github.io/htw/paper.html){width="900" height="600"}

```{r}
pacman::p_load(tidyverse,knitr,kableExtra)

### 2023-10-19 Manuscript/pre_sections/pre_html.qmd
fix docx and html. Update htw with embed

<div style="text-align: center; margin-top: 300px;">
  _____________________________  Robert L. Goldstone<br><br>
  _____________________________  Robert Nosofsky<br><br>
  _____________________________  Peter Todd<br><br>
  _____________________________  Mike Jones
</div>

>>>>

<div style="text-align: center; margin-top: 300px;">
  _____________________________  Robert L. Goldstone, PhD<br><br>
  _____________________________  Robert Nosofsky, PhD<br><br>
  _____________________________  Peter Todd, PhD<br><br>
  _____________________________  Mike Jones, PhD
</div>

### 2023-10-19 paper.qmd
fix docx and html. Update htw with embed

  <a class="btn btn-info btn-sm mb-1" target="_blank" href="/Manuscript/manuscript.md">
  <iconify-icon inline="" icon="fa6-solid:file-word"></iconify-icon> &ensp;md <small>(download)</small>
  </a>

>>>>

  <!-- <a class="btn btn-info btn-sm mb-1" target="_blank" href="/Manuscript/manuscript.md">
  <iconify-icon inline="" icon="fa6-solid:file-word"></iconify-icon> &ensp;md <small>(download)</small>
  </a> -->
